Multi-Robot Probabilistic Mapping and Exploration

### 2018-08-02 Dissertation/Thesis/tex/conclusions.tex
added Final Papers folder for unchanging final papers

The contributions in probabilistic occupancy grid mapping and autonomous exploration are extended in several ways. Probabilistic mapping and autonomous exploration are extended from 2D to 3D with two approaches: projecting a 3D map onto a 2D plane for exploration, or using the full 3D map for entropy predictions. This concept is also extended to cooperative multi-vehicle autonomous exploration, where a bidding-based framework coordinates robotic efforts to understand the map. The approach follows a receding horizon, which improves collision-avoidance and substantially reduces unnecessary robotic actions. Furthermore, this approach is extended to autonomous patrol, where an exponential map degradation incentivizes robot team members to periodically revisit areas. These extensions to occupancy grid mapping and autonomous exploration are demonstrated with numerous simulations and experimental results.

>>>>

The contributions in probabilistic occupancy grid mapping and autonomous exploration are extended in several ways. Probabilistic mapping and autonomous exploration are extended from 2D to 3D with two approaches: projecting a 3D map onto a 2D plane for exploration, or using the full 3D map for entropy predictions. This concept is also extended to cooperative multi-vehicle autonomous exploration, where a bidding-based framework coordinates robotic efforts to understand the map. The approach follows a receding horizon, which improves collision-avoidance and substantially reduces unnecessary robotic actions. Furthermore, this approach is extended to autonomous patrol, where exponential map degradation incentivizes robot team members to periodically revisit areas. These extensions to occupancy grid mapping and autonomous exploration are demonstrated with numerous simulations and experimental results.

### 2018-08-02 Dissertation/Thesis/tex/frontmatter.tex
updated section 7.4 of dissertation to bring figures together with section 7.3, started defense presentation
added Final Papers folder for unchanging final papers

James Hahn\\
Department of Computer Science\\
The George Washington University\\
Committee Chair\\

Taeyoung Lee\\
Department of Mechanical and Aerospace Engineering\\
The George Washington University\\ 
Committee Member\\ % remember to add a space between committee members

Robert Pless\\
Department of Computer Science\\
The George Washington University\\
Committee Member\\

Chung Hyuk Park\\
Department of Biomedical Engineering\\
The George Washington University\\ 
Committee Member\\

Zhuming Ai\\
Information Management and Decision Architectures\\
U.S. Naval Research Laboratory\\ 
Committee Member

@@

\phdgrad{July 13, 2018}
\defensedate{July 13, 2018}
% Year of completion for copyright page and perhaps other places
\year=2018

@@

% ------------ TABLE OF CONTENTS ----------------------
% Commands to hide or show lists of figures, tables, etc.
\showlistoffigures
\showlistoftables
\hidenomenclature

@@

% acronymns and symbols are basically the same, but there are two provided 
% locations where they can show up
\setabbreviationstyle[acronym]{long-short}
\setabbreviationstyle[abbreviation]{long-short}
\makeglossaries
% you can hide/show the glossaries page
\showglossarieslistofabbreviations
\showglossarieslistofsymbols
\showglossariesglossaryofterms

% acronyms defined in glossaries
\newabbreviation{lidar}{LIDAR}{Light Detection and Ranging}
% defining abbreviations like this allows for autocompletion
\newglossaryentry{filo}{
    name={FILO},
    type=\glsxtrabbrvtype,
    description={first in last out},
    first={first in last out (FILO)}
}

% glossary entries
\newglossaryentry{linux}{
    name=Linux,
    description={is a generic term referring to the family of Unix-like computer operating systems that use the Linux kernel},
    plural=Linuces
}

\newglossaryentry{matrix}{
    name={matrix},
    plural={matrices},
    description={rectangular array of quantities}
}

% symbols
\newglossaryentry{M}{
    type=symbols,
    name={\ensuremath{M}},
    sort=M,
    description={a \gls{matrix}}
}

\newglossaryentry{F}{
    type=symbols,
    name={\ensuremath{F}},
    sort=F,
    description={External Force}
}
% Some abstract text
\abstract{
This dissertation focuses on robotic mapping and exploration of uncertain environments. Computational algorithms are developed to provide complete stochastic information of the environments. These algorithms are designed for real-time implementation for robotic autonomy.

>>>>

\vspace*{0.05\textwidth}
Taeyoung Lee, Associate Professor of Mechanical and Aerospace Engineering, Dissertation Director\\

James Hahn, Professor of Computer Science, Committee Member\\

Robert Pless, Professor of Computer Science, Committee Member\\

Chung Hyuk Park, Assistant Professor of Biomedical Engineering, Committee Member\\

Zhuming Ai, Computer Engineer, U.S. Naval Research Laboratory, Committee Member

@@

\phdgrad{August 31, 2018}
\defensedate{July 13, 2018}
% Year of completion for copyright page and perhaps other places
\year=2018

@@

% ------------ TABLE OF CONTENTS ----------------------
% Commands to hide or show lists of figures, tables, etc.
\showlistoffigures
\hidelistoftables
\hidenomenclature

@@

% acronymns and symbols are basically the same, but there are two provided 
% locations where they can show up
\setabbreviationstyle[acronym]{long-short}
\setabbreviationstyle[abbreviation]{long-short}
\makeglossaries
% you can hide/show the glossaries page
\hideglossarieslistofabbreviations
\hideglossarieslistofsymbols
\hideglossariesglossaryofterms

\abstract{
This dissertation focuses on robotic mapping and exploration of uncertain environments. Computational algorithms are developed to provide complete stochastic information of the environments. These algorithms are designed for real-time implementation for robotic autonomy.
